**Weight Lifting Prediction**

**By: Mnguyen747**

**---**

The idea and general approach will be as follows:
1. Subset data for only columns that have less than 60% of NA's. Then split the data into train/test/prediction set.
2. Train/test a random forest model on the training/testing data sets.
3. Run the data on the prediction set.

**1. Subset data for only columns that have less than 60% of NA's. Then split the data into train/test/prediction set.**

```{r}

rm(list=ls())

library(dplyr)

training <- tbl_df(read.csv(url("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"), na.strings=c("NA","#DIV/0!","")))
prediction_set <- tbl_df(read.csv(url("http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"), na.strings=c("NA","#DIV/0!","")))

#Subsetting only relevant columns
training <- select(training,c(8:ncol(training)))
prediction_set <- select(prediction_set,c(8:ncol(prediction_set)))
col_final <- vector()

for(i in 1:ncol(training)){
  if( (sum(is.na(training[,i]))/nrow(training)) <= .6){
    col_final <- append(col_final,i)
  }
}

training <- select(training, c(col_final))
prediction_set <- select(prediction_set, c(col_final))
prediction_set <- select(prediction_set, c(1:(ncol(prediction_set)-1)))

#Now breaking training into testing/training set.

index <- sample(c(1:nrow(training)),.75*nrow(training), replace = FALSE)
training_final <- training[index,]
testing_final <- training[-index,]

rm(training,col_final,i,index)

```

**2. Train/test a random forest model on the training/testing data sets.**

```{r}

library(randomForest)
library(caret)

rf_fit <- randomForest(classe ~. , data=training_final)
rf_pred <- predict(rf_fit, testing_final, type = "class")

confusionMatrix(rf_pred,testing_final$classe)

#Tried & True, Random Forest Works

```

**3. Run the data on the prediction set.**

```{r}

rf_pred <- predict(rf_fit, prediction_set, type = "class")
print(rf_pred)

#Quiz Score: 20/20 :)

```

